The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-11-24 smurf_paper.tex
Add POL-2 and FTS-2 references to para 1 and use ISO date order.

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the the 15-m
James Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
can simultaneously image the sky in two broad bands centered over 450
and 850\,\micron. Ultimately, the instrument will also be equipped
with a Fourier transform spectrometer (FTS), and a polarimeter
(POL). This paper describes the Submillimetre User Reduction Facility,
SMURF, a software package for reducing the imaging data, with an
emphasis on data taken during the SCUBA-2 Shared Risk Observing period
(S2SRO) which took place from February to April of 2010. The reduction
of FTS and POL data will be described at a later date once these
additional instruments have been commissioned.

>>>>

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the the 15-m
James Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
can simultaneously image the sky in two broad bands centered over 450
and 850\,\micron. Ultimately, the instrument will also be equipped
with a Fourier transform spectrometer \citep[FTS-2,][]{gom2010}, and a polarimeter
\cite[POL-2,][]{bastien2005}. This paper describes the Submillimetre User Reduction Facility,
SMURF, a software package for reducing the imaging data, with an
emphasis on data taken during the SCUBA-2 Shared-Risks Observing period
(S2SRO) which took place from 2010 February 11 to 2010 March 25. The reduction
of FTS-2 and POL-2 data will be described at a later date once these
additional instruments have been commissioned.
